\documentclass[12pt]{article}
\nocite{*}
\usepackage{newtxtext,newtxmath}

\usepackage{graphics}
\usepackage{tcolorbox}
\usepackage{color}
\usepackage[margin=0.5in]{geometry}
\usepackage[hyphens]{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{comment}
\usepackage{pdfpages}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[font=small]{caption,subcaption}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[normalem]{ulem}
\usepackage{titling}
\usepackage{hyperref}
\usepackage{floatrow}
\setlength{\droptitle}{-8em}

%\titlespacing\section{0pt}{8pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
%\titlespacing\subsection{0pt}{8pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
%\titleformat*{\section}{\large\bfseries}
%\titleformat*{\subsection}{\normalsize\bfseries}

\titleformat{\section}{\normalfont\fontsize{12}{15}\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{0.2in}{0in}
\pagenumbering{gobble}

\title{}
\author{\textbf{\LARGE Matthew Thomas Pisano}} 
\date{}

\begin{document}
\pagestyle{plain}

\begin{tcolorbox}[width=\linewidth, sharp corners=all, colback=white!90!green, colframe=black]
    
    \begin{center}
        \textbf{\LARGE Matthew Thomas Pisano}\\
        \vspace{0.1in}
        (845)-706-0677 \hspace*{0.3in}
        \href{mailto:matthewpisano14@gmail.com}{matthewpisano14@gmail.com} \hspace*{0.5in}
        \href{https://www.linkedin.com/in/matthew-pisano/}{LinkedIn: matthew-pisano}
    \end{center}
    
\end{tcolorbox}

\vspace{0.1in}

\hspace*{-0.3in}
\textbf{Research Objective:} To create novel alignment strategies for artificially intelligent agents.

\vspace{0.1in}

\hspace*{-0.3in}
\textbf{GitHub:} \href{https://github.com/matthew-pisano}{matthew-pisano} Many of my open-source projects and contributions.

\hspace*{-0.3in}
\textbf{Portfolio Website:} \href{https://matthewpisano.com}{matthewpisano.com} for a more detailed look at my notable projects and research.

\section*{Skills and Experience:}
\begin{itemize}
    \itemsep0em
    \item \textbf{Research (2 Years):} Multiple conference acceptances, academic talk invitations, work in research labs.
    \item \textbf{Machine Learning (2 Years):} Transformer models, prompt engineering, RL, NLP, ASR, PyTorch, CUDA.
    \item \textbf{Python Programming (5 Years):} PyTorch, HuggingFace, data analysis, fine-tuning.
    \item \textbf{Software Development (3 Years):} DevOps in a professional, team setting, CI/CD. 
    \item \textbf{AWS (4 Years):} Cloudformation, EC2, Lambda, S3.
    \item \textbf{Java Programming (5 Years):} Application and Android development, program analysis.
    \item \textbf{Web Development (5 Years):} React.js, Node.js, responsive design, DB management.
    \item \textbf{Awards and Certifications:} Eagle Scout, SUNY NP outstanding graduate, $1^{st}$ place at Mega-Ace.
\end{itemize}

\section*{Education:}
\begin{itemize}
    \itemsep0em
    \item \textbf{Rensselaer Polytechnic Institute}, 110 8th St, Troy, NY. (\textit{2023-2024}) Master of Science in Computer Science, thesis on artificial intelligence alignment and NLP.  4.0 GPA, awarded TA position and scholarship.
    \item \textbf{SUNY New Paltz}, 1 Hawk Dr, New Paltz, NY. (\textit{2021-2022}) Bachelor of Science in Computer Science, Minor in Applied Mathematics, and undergraduate research. 4.0 GPA, and Outstanding Graduate honor.
\end{itemize}

\section*{Research and Publications:}
\begin{itemize}
    \itemsep0em
    
    \item \textbf{Bergeron: Combating Adversarial Attacks through a Conscience-Based Alignment Framework}.  A weak-to-strong generalization framework for alignment.  Involves an LLM acting as the ``conscience'' of a stronger LLM.  Submitted to \textit{COLM} 2024.  \href{https://arxiv.org/abs/2312.00029}{ArXiv: 2312.00029}
    
    \item \textbf{Moral High Ground: A Text-Based Games Benchmark for Moral Evaluation}, under \textit{IBM}.  A novel benchmark for evaluating the moral reasoning abilities of LLMs through conversational text-based games.
    
    \item \textbf{PredictChain: Empowering Collaboration and Data Accessibility for AI in an Algorand Blockchain-based Marketplace}.  Research article on the development of \textit{PredictChain}, a decentralized machine learning marketplace.  $1^{st}$ place global hackathon winner.  Presented at \textit{ChainScience} 2023. \href{https://arxiv.org/abs/2307.15168}{ArXiv: 2307.15168}
    
    \item \textbf{Large Acoustic Modeling for ASR}, under the \textit{RPI AIRC Lab}. Research into improving the performance of modern ASM models by using a variety of techniques such as model fine-tuning and corrector LLMs.
    
\end{itemize}

\section*{Work Experience:}
\begin{itemize}
    \itemsep0em 
    \item \textbf{IBM Research}, 1101 Kitchawan Rd, Yorktown Heights, NY: Research Extern through RPI. (\textit{2023}) Research into LLM alignment using moral principles through fine-tuning on text-based games.
    
    \item \textbf{Cyber Guardian Consulting Group}, 63 John St, Kingston, NY: Software Developer. (\textit{2020-204}) Extensive use of AWS, custom SaaS solutions, full stack web development, backup and restoration software, development in Python, PowerShell, and Javascript frameworks.
    
    \item \textbf{Rensselaer Polytechnic Institute}, 110 8th St, Troy, NY: Computer Science Teaching Assistant. (\textit{2023-2024}) Assist students, grade assignments for the \textit{Principles of Software} and \textit{Data Structures} classes.
\end{itemize}
\end{document}
